### 2022-06-14 main/chapter_2ljets.tex
clarify interesting sentence more
add c1n2 200,100 note; remove atlas tag from some figures

\FloatBarrier
\subsection{Low}
\label{sec:2ljets_low}

In Low regions, which have $\metsig \in 6\textrm{--}12$, the $\zjets$
background becomes a large since its fake $\met$, which arises from
from mismeasurements or rare interactions, is no longer eliminated.
Similarly, backgrounds from $\ttbar$ increase; the selections inherited from
Intermediate regions to suppress $\ttbar$ need supplementing.

@@

Modelling multi-jet QCD is hard.
This deficit was therefore blamed on multi-jet QCD modelling, and resolved by
retreating to two-jet events.
It is interesting , however, that the two-jet SR-Low did eventually observe a
comparable deficit.

>>>>

\FloatBarrier
\subsection{Low}
\label{sec:2ljets_low}
In Low regions, which have $\metsig \in 6\textrm{--}12$, the $\zjets$
background becomes a large since its fake $\met$, which arises from
from mismeasurements or rare interactions, is no longer eliminated.
Similarly, backgrounds from $\ttbar$ increase; the selections inherited from
Intermediate regions to suppress $\ttbar$ need supplementing.

These regions target signal models with small mass splittings which still
exceed the masses of electroweak bosons.
In particular, we aim to test C1N2($200$, $100$) as a light, on-shell
benchmark which has not previously been excluded in this channel.

@@

Modelling multi-jet QCD is hard.
This deficit was therefore blamed on multi-jet QCD modelling, and resolved by
retreating to two-jet events.
It is interesting , however, that the two-jet SR-Low eventually observed a
comparable deficit.
